%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Shifan Xu}, Alvin Lu, and Yongshan Ding. ``Fat-Tree QRAM: A High-Bandwidth Shared Quantum Random Access Memory for Parallel Queries.'' Proceedings of the 30th ACM International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS), Volume 2. 2025.}

    \cvpub{Samuel Stein, \textbf{Shifan Xu}, Andrew W. Cross, Theodore J. Yoder, Ali Javadi-Abhari, Chenxu Liu, Kun Liu, Zeyuan Zhou, Charles Guinn, Yufei Ding, Yongshan Ding, and Ang Li. ``HetEC: Architectures for Heterogeneous Quantum Error Correction Codes.'' Proceedings of the 30th ACM International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS), Volume 2. 2025.}

   
    \cvpub{\textbf{Shifan Xu}, Connor T. Hann, Ben Foxman, Steven M. Girvin, and Yongshan Ding. ``Systems Architecture for Quantum Random Access Memory.'' In Proceedings of the 56th Annual IEEE/ACM International Symposium on Microarchitecture (MICRO), pp. 526--538. 2023.}

\end{cvpubs}


%---------------------------------------------------------
\cvsubsection{Preprints}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{Kun Liu, \textbf{Shifan Xu}, Tomas Jochym-O'Connor, Zhiyang He, Shraddha Singh, and Yongshan Ding. ``In-Situ Simultaneous Magic State Injection on Arbitrary CSS qLDPC Codes.'' arXiv preprint arXiv:2604.05126 (2026).}

    \cvpub{\textbf{Shifan Xu}, Kun Liu, Patrick Rall, Zhiyang He, and Yongshan Ding. ``Distilling Magic States in the Bicycle Architecture.'' arXiv preprint arXiv:2602.20546 (2026).}

    \cvpub{Adrian Harkness, Shuwen Kan, Chenxu Liu, Meng Wang, John M. Martyn, \textbf{Shifan Xu}, Diana Chamaki, Ethan Decker, Ying Mao, Luis F. Zuluaga, Tam\'as Terlaky, Ang Li, and Samuel Stein. ``FTCircuitBench: A Benchmark Suite for Fault-Tolerant Quantum Compilation and Architecture.'' arXiv preprint arXiv:2601.03185 (2026).}

    \cvpub{D. K. Weiss, \textbf{Shifan Xu}, Shruti Puri, Yongshan Ding, and Steven M. Girvin. ``Faulty towers: recovering a functioning quantum random access memory in the presence of defective routers.'' arXiv preprint arXiv:2411.15612 (2024).}
\end{cvpubs}

%---------------------------------------------------------
