%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Advisor: Dr. Yongshan Ding} % Advisor
    {Yale University - Applied Physics Department} % Institution
    {New Haven, CT, USA} % Location
    {Sep. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Architectural Improvements in Quantum Random Access Memory}
        \item {Practical Quantum Memory Architecture in NISQ and Fault-tolerant Era}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisor: Dr. Ang Li} % Advisor
    {Pacific Northwest National Laboratory (PNNL)} % Institution
    {Richland, WA, USA} % Location
    {Jun. 2025 - Aug. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Project: Quantum Secure Query}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisor: Dr. Tianjue Min} % Advisor
    {Nanjing University - Physics Department} % Institution
    {Nanjing, China} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Graduation Thesis Project: ``Analysis of Background Noise in $p\bar{p}$ Collision Experiments Based on the K-Nearest Neighbors (KNN) Algorithm''}
      \end{cvitems}
    }

  \cventry
    {Advisor: Dr. Sheng Xu} % Advisor
    {UC San Diego - Department of NanoEngineering } % Institution
    {(remote) San Diego, CA, USA} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Project: Circuit Design for Flexible Ultrasonic Array}
      \end{cvitems}
    }

  \cventry
    {Advisor: Dr. Xin Li, Dr. Minghui Lu} % Advisor
    {Nanjing University - Engineering Department} % Institution
    {Nanjing, China} % Location
    {2019-2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Project: Preparation and Design of Auxetic Metamaterials}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Supervisor: Prof. Sihui Wang} % Advisor
    {Nanjing University - Physics Department} % Institution
    {Nanjing, China} % Location
    {2018-2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Project: Metal Powder Spectra Analysis}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
